Data Wrangling and Statistical Analysis of Assessment of Abundance, Aggregation, and Web Placement of *Agelenopsis pennsylvanica*

### 2022-11-28 data_analysis.Rmd
More work on the manuscript

Tree cover is **significantly higher in the urban forest** than the urban center (z = -14.50, df = 1, 20, p < 0.001). The means and SE's are 47.15 ± 2.17 % for the urban forest and 1.58 ± 0.36 % for the urban center.

@@

Impervious cover is **significantly higher in the urban center** than the urban forest (z = 14.51, df = 1, 20, p < 0.001). The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.53 % for the urban center.

```{r stats_graphs_tdr, echo = FALSE}
tdr <- glm(log_tdr ~ Location, family = "poisson", data = sites)
summary(tdr)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(log_tdr),
            se = plotrix::std.error(log_tdr))

@@

ggplot(sites, aes(x = Location, y = exp(log_tdr))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 1400), breaks = c(0, 200, 400, 600, 800, 1000, 1200, 1400)) +
  theme_classic() +
  ylab("Road Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=1400, label="N. S.", color="black", size = 10)
```

@@

There is **no difference** in road disturbance between the urban forest and urban center (z = 1.403, df = 1, 20, p = 0.161). The means and SE's are `r exp(3.97)` ± `r exp(0.630)` vehicles/day/m for the urban forest and `r exp(5.27)` ± `r exp(0.663)` vehicles/day/m for the urban center.

```{r stats_graphs_tdh, echo = FALSE}
tdh <- glm(log_tdh ~ Location, family = "poisson", data = sites)
summary(tdh)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(log_tdh),
            se = plotrix::std.error(log_tdh))

@@

ggplot(sites, aes(x = Location, y = exp(log_tdh))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 250), breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_classic() +
  ylab("Highway Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=250, label="N. S.", color="black", size = 10)
```

@@

There is **no difference** in highway disturbance between the urban forest and urban center (z = 0.530, df = 1, 20, p = 0.596). The means and SE's are `r exp(3.52)` ± `r exp(0.593)` vehicles/day/m for the urban forest and `r exp(3.96)` ± `r exp(0.574)` vehicles/day/m for the urban center.

```{r stats_graphs_plant, echo = FALSE}
plant <- glm(log_TotalSub ~ Location, family = "poisson", data = sites)
summary(plant)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(log_TotalSub),
            se = plotrix::std.error(log_TotalSub))

@@

ggplot(sites, aes(x = Location, y = exp(log_TotalSub))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
  theme_classic() +
  ylab("Plant Species Richness \n[species/site]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=25, label="*", color="black", size = 10)
```

@@

Plant species richness is **significantly higher in the urban forest** than the urban center (z = -2.430, df = 1, 20, p = 0.015). The means and SE's are `r exp(2.50)` ± `r exp(0.500)` species for the urban forest and `r exp(1.09)` ± `r exp(0.302)` species for the urban center.

@@

Spectral radiance is **significantly higher in the urban center** than the urban forest (z = 3.079, df = 1, 20, p = 0.002). The means and SE's are 137.44 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153.39 ± 3.58 Watts/(m² * sr * µm) for the urban center.

@@

Light radiance is **significantly higher in the urban center** than the urban forest (z = 22.46, df = 1, 20, p < 0.001). The means and SE's are 5.89 ± 0.77 mcd/m² for the urban forest and 116.90 ± 3.12 mcd/m² for the urban center.

```{r stats_graphs_patch, echo = FALSE}
patch <- glm(log_patch ~ Location, family = "poisson", data = sites)
summary(patch)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(log_patch),
            se = plotrix::std.error(log_patch))

@@

ggplot(sites, aes(x = Location, y = exp(log_patch))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 130310), breaks = c(0, 20000, 40000, 60000, 80000, 100000, 120000)) +
  theme_classic() +
  ylab("Patch Area [mm²]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=130310, label="***", color="black", size = 10)
```

@@

Patch area is **significantly higher in the urban forest** than the urban center (z = -3.599, df = 1, 20, p < 0.001). The means and SE's are `r exp(10.52)` ± `r exp(1.026)` mm² for the urban forest and `r exp(6.08)` ± `r exp(0.712)` mm² for the urban center.

@@

Total road length is **significantly higher in the urban center** than the urban forest (z = 20.89, df = 1, 20, p < 0.001). The means and SE's are 15.67 ± 1.25 m for the urban forest and 93.03 ± 2.78 m for the urban center.

@@

# Tree
nd <- data.frame(log_TotalSub = mean(near_forest$log_TotalSub), 
                 log_tdr = mean(near_forest$log_tdr),
                 log_tdh = mean(near_forest$log_tdh),
                 tree100m = seq(31.37, 65.87, 0.35))
predicted.distance <- augment(top_model_wd_f, 
                              newdata = nd, 
                              se_fit = TRUE)
dist_forest_tree <- ggplot(near_forest, aes(x = (tree100m), y = log(RetreatDist))) + 
  geom_point(color = "grey", 
             size = 1) +
  geom_line(aes(x = (tree100m), y = .fitted), 
            size = 1, 
            color = colorf, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = log(tree100m), 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = colorf, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(min(log(near_forest$RetreatDist)), max(log(near_forest$RetreatDist)) + 0.1 * diff(range(log(near_forest$RetreatDist))))) +  
  theme_classic() +
  xlab("Percent Tree Cover [%]") +
  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank()) +
  annotate(geom = "text", x = min((predicted.distance$tree100m)) + diff(range((predicted.distance$tree100m)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)

@@

```{r pred_location, fig.width = 6.85, dpi = 300}
mean_se1 <- c("Mean ± Std. Error", "Wilderness Park \nUrban Forest", "47.15 ± 2.17", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.77", "12.18 ± 1.65", "37,049.12 ± 2.79", "52.98 ± 1.88", "33.78 ± 1.81", "15.67 ± 1.25")
mean_se2 <- c("Mean ± Std. Error", "UNL City Campus \n Urban Center", "1.58 ± 0.36", "76.52 ± 2.53", "153.39 ± 3.58", "116.90 ± 3.12", "2.97 ± 1.35", "437.03 ± 2.04", "194.42 ± 1.94", "52.46 ± 1.78", "93.03 ± 2.78")
pred_location <- data.frame(mean_se1, mean_se2)
rownames(pred_location) <- c("", " ", "Percent Tree Cover [%]", "Percent Impervious Cover [%]", "Spectral Radiance [Watts/(m² * sr * µm)]", "Artificial Night Sky Radiance [mcd/m²]", "Plant Species Richness", "Patch Area [m²]", "Road Disturbance [vehicles/day/m]", "Highway Disturbance [vehicles/day/m]", "Total Road Length [m]")
names <- rownames(pred_location)
rownames(pred_location) <- seq(1:nrow(pred_location))
pred_location <- cbind(names, pred_location)
colnames(pred_location) <- c(" ", "Mean ± Std. Error", "Mean ± Std. Error")
flextable(pred_location[ ,1:3]) %>% 
  delete_part(part = "header") %>% 
  autofit() %>% 
  merge_h(part = "body") %>% 
  bold(bold = TRUE,i = c("1", "2"), part = "body") %>% 
  hline(i = c("1", "2", "11"), part = "body", border = officer::fp_border(width = 2)) %>% 
  hline_top(part = "body", border = officer::fp_border(width = 2)) %>% 
  fontsize(size = 10, part = "all") %>% 
  align(align = "center", part = "all") %>% 
  set_caption("") %>% 
  save_as_image(path = here::here("manuscript/figures/pred_location.png"))
```

>>>>

Tree cover is **significantly higher in the urban forest** than the urban center (z = -14.50, df = 1, 21, p < 0.001). The means and SE's are 47.15 ± 2.17 % for the urban forest and 1.58 ± 0.36 % for the urban center.

@@

Impervious cover is **significantly higher in the urban center** than the urban forest (z = 14.51, df = 1, 21, p < 0.001). The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.53 % for the urban center.

```{r stats_graphs_tdr, echo = FALSE}
tdr <- glm(Traffic_Dist_Road ~ Location, family = "poisson", data = sites)
summary(tdr)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(Traffic_Dist_Road),
            se = plotrix::std.error(Traffic_Dist_Road))

@@

ggplot(sites, aes(x = Location, y = Traffic_Dist_Road)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = (rate - SE), 
                  ymax = (rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 1400), breaks = c(0, 200, 400, 600, 800, 1000, 1200, 1400)) +
  theme_classic() +
  ylab("Road Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=1400, label="***", color="black", size = 10)
```

@@

**Road disturbance is higher in the urban center** than the urban forest (z = 39.19, df = 1, 21, p < 0.001). The means and SE's are 104 ± 3.23 vehicles/day/m for the urban forest and 398 ± 5.76 vehicles/day/m for the urban center.

```{r stats_graphs_tdh, echo = FALSE}
tdh <- glm(Traffic_Dist_Highway ~ Location, family = "poisson", data = sites)
summary(tdh)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(Traffic_Dist_Highway),
            se = plotrix::std.error(Traffic_Dist_Highway))

@@

ggplot(sites, aes(x = Location, y = (Traffic_Dist_Highway))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = (rate - SE), 
                  ymax = (rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 250), breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_classic() +
  ylab("Highway Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=250, label="***", color="black", size = 10)
```

@@

**Highway disturbance is higher in the urban center** than the urban fores (z = 9.388, df = 1, 21, p < 0.001). The means and SE's are 35.6 ± 1.89 vehicles/day/m for the urban forest and 65.0 ± 2.33 vehicles/day/m for the urban center.

```{r stats_graphs_plant, echo = FALSE}
plant <- glm(TotalSub ~ Location, family = "poisson", data = sites)
summary(plant)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(TotalSub),
            se = plotrix::std.error(TotalSub))

@@

ggplot(sites, aes(x = Location, y = (TotalSub))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = (rate - SE), 
                  ymax = (rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
  theme_classic() +
  ylab("Plant Species Richness \n[species/site]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=25, label="***", color="black", size = 10)
```

@@

Plant species richness is **significantly higher in the urban forest** than the urban center (z = -7.674, df = 1, 21, p < 0.001). The means and SE's are 13.30 ± 1.153 species for the urban forest and 3.33 ± 0.527 species for the urban center.

@@

Spectral radiance is **significantly higher in the urban center** than the urban forest (z = 3.079, df = 1, 21, p = 0.002). The means and SE's are 137.44 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153.39 ± 3.58 Watts/(m² * sr * µm) for the urban center.

@@

Light radiance is **significantly higher in the urban center** than the urban forest (z = 22.46, df = 1, 21, p < 0.001). The means and SE's are 5.89 ± 0.77 mcd/m² for the urban forest and 116.90 ± 3.12 mcd/m² for the urban center.

```{r stats_graphs_patch, echo = FALSE}
patch <- glm(patch_area_mm ~ Location, family = "poisson", data = sites)
summary(patch)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(patch_area_mm),
            se = plotrix::std.error(patch_area_mm))

@@

ggplot(sites, aes(x = Location, y = (patch_area_mm))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = (rate - SE), 
                  ymax = (rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 130310), breaks = c(0, 20000, 40000, 60000, 80000, 100000, 120000)) +
  theme_classic() +
  ylab("Patch Area [mm²]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=130310, label="***", color="black", size = 10)
```

@@

Patch area is **significantly higher in the urban forest** than the urban center (z = -374.2, df = 1, 21, p < 0.001). The means and SE's are 46,294.7 ± 68.040 mm² for the urban forest and 653.8 ± 7.381 mm² for the urban center.

@@

Total road length is **significantly higher in the urban center** than the urban forest (z = 20.89, df = 1, 21, p < 0.001). The means and SE's are 15.67 ± 1.25 m for the urban forest and 93.03 ± 2.78 m for the urban center.

@@

# Tree
nd <- data.frame(log_TotalSub = mean(near_forest$log_TotalSub), 
                 log_tdr = mean(near_forest$log_tdr),
                 log_tdh = mean(near_forest$log_tdh),
                 tree100m = seq(31.37, 65.87, 0.35))
predicted.distance <- augment(top_model_wd_f, 
                              newdata = nd, 
                              se_fit = TRUE)
dist_forest_tree <- ggplot(near_forest, aes(x = (tree100m), y = log(RetreatDist))) + 
  geom_point(color = "grey", 
             size = 1) +
  geom_line(aes(x = (tree100m), y = .fitted), 
            size = 1, 
            color = colorf, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = (tree100m), 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = colorf, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(min(log(near_forest$RetreatDist)), max(log(near_forest$RetreatDist)) + 0.1 * diff(range(log(near_forest$RetreatDist))))) +  
  theme_classic() +
  xlab("Percent Tree Cover [%]") +
  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank()) +
  annotate(geom = "text", x = min((predicted.distance$tree100m)) + diff(range((predicted.distance$tree100m)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)

@@

```{r pred_location, fig.width = 6.85, dpi = 300}
mean_se1 <- c("Mean ± Std. Error", "Wilderness Park \nUrban Forest", "47.15 ± 2.17", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.77", "13.30 ± 1.15", "46,294.7 ± 68.040", "104 ± 3.23", "35.6 ± 1.89", "15.67 ± 1.25")
mean_se2 <- c("Mean ± Std. Error", "UNL City Campus \n Urban Center", "1.58 ± 0.36", "76.52 ± 2.53", "153.39 ± 3.58", "116.90 ± 3.12", "3.33 ± 0.53", "116.90 ± 3.12", "398 ± 5.76", "65.0 ± 2.33", "93.03 ± 2.78")
pred_location <- data.frame(mean_se1, mean_se2)
rownames(pred_location) <- c("", " ", "Percent Tree Cover [%]", "Percent Impervious Cover [%]", "Spectral Radiance [Watts/(m² * sr * µm)]", "Artificial Night Sky Radiance [mcd/m²]", "Plant Species Richness", "Patch Area [m²]", "Road Disturbance [vehicles/day/m]", "Highway Disturbance [vehicles/day/m]", "Total Road Length [m]")
names <- rownames(pred_location)
rownames(pred_location) <- seq(1:nrow(pred_location))
pred_location <- cbind(names, pred_location)
colnames(pred_location) <- c(" ", "Mean ± Std. Error", "Mean ± Std. Error")
flextable(pred_location[ ,1:3]) %>% 
  delete_part(part = "header") %>% 
  autofit() %>% 
  merge_h(part = "body") %>% 
  bold(bold = TRUE,i = c("1", "2"), part = "body") %>% 
  hline(i = c("1", "2", "11"), part = "body", border = officer::fp_border(width = 2)) %>% 
  hline_top(part = "body", border = officer::fp_border(width = 2)) %>% 
  fontsize(size = 10, part = "all") %>% 
  align(align = "center", part = "all") %>% 
  set_caption("") %>% 
  save_as_image(path = here::here("manuscript/figures/pred_location.png"))
```
